### 2021-08-13 doc/thesis/chapters/results.tex
todo
fir filter

with TB

@@

>>>>

The FIR filter is one of the main DSP blocks of the design, as it is used in multiple instances throughout the design.
Therefore, its implementation was done with special care, in order to guarantee its correct functionality.
Consequently, a unit test is implemented in the testbench, which is also included in the listed number of implementation hours.\\

For the \cplusplus\ version, a code example for an FIR filter, which is provided by Xilinx HLS, is taken and modified for the present purpose.
The VHDL variant is taken from an older DSP project, which was previously developed during a university course.
However, the integration and testbench code is developed for this project, specifically.
Here, the HLS implementation took significantly longer, because of the limited knowledge regarding the usage of an AXI stream interface.
It is the first time in the project, that this type of interface is applied in the IP design and used in the testbench.
The VHDL implementation was straightforward in comparison.
The testbenches compare the FIR filters' output with the Matlab model's pilot tone output.
Both variants match the output results of the Matlab model successfully.

@@

todo \\
